%!TEX TS-program = pdflatex
\documentclass{phiha-review}
\usepackage{amsmath,amssymb,amsthm}

\usepackage[sort&compress]{natbib}

\usepackage[utf8]{inputenc}
\usepackage[vietnamese]{babel}
\usepackage{graphicx}

\usepackage[a4paper, total={6.4in, 9in}]{geometry}
\usepackage{lipsum}

\RequirePackage{fix-cm} % arbitrary font scaling
\DeclareMathSizes{10}{10}{7}{3}


\newtheorem{theorem}{Theorem}[section]
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

%%% Useful abbreviations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\cal{\mathcal}
\def \ud{\underline }
\def\id{{\indent }}
\def\f{\frac}
\def\non{{\noindent}}
\def\leq{\leqslant} 
\def\rar{\rightarrow}
\def\Rar{\Rightarrow}
\def\ti{\times}
\def\r{\hro{R}}
\def\e{\cal{E}}
\def\de{\delta}
\def\ep{\varepsilon}
\def\Ep{\epsilon}
\def\De{\Delta}
\def\ift{\infty}
\def\hro{\mathbb}
\def\ho{\mathcal}
\def\E{\mathcal{E}}
\def\A{\mathcal{A}}
\def\N{\mathbb{N}}
\def\vk{\vskip 0.2cm}
\def\con{\subset}
\def\Con{\subseteq}
\def\td{\Leftrightarrow}
\def\df{\frac}
\def\to{\mapsto}
\def\om{\omega}
\def\a{\alpha}
\def\hA{\hat{A}}
\def\tA{\tilde{A}}
\def\dA{\delta A}
\def\lb{\lambda}
\def\to{\mapsto}
\def\a{\alpha}
\def\b{\beta}
\def\ga{\gamma}
\def\Ga{\Gamma}
\def\Si{\Sigma}
\def\dA{\delta A}
\def\lb{\lambda}
\def\Lb{\Lambda}
\def\tE{\tilde{E}} 
\def\tA{\tilde{A}} 
\def\tB{\tilde{B}}
\def\tM{\tilde{M}}  
\def\tb{\bar{t}}
\def\ub{\bar{u}} 
\def\taub{\bar{\tau}} 
\def\hE{\hat{E}}
\def\hB{\hat{B}}
\def\hP{\hat{P}}
\def\hQ{\hat{Q}}
\def\DD{\mathbb{D}}
\def\tf{\tilde{f}}
\def\tx{\tilde{x}}
\def\I{\mathbb{I}}
\def\A{\cal{A}}
\def\B{\cal{B}}
\def\C{\cal{C}}
\def\D{\cal{D}}
\def\F{\cal{F}}
\def\R{\cal{R}}
\def\K{\cal{K}}
\def\M{\cal{M}}
\def\P{\cal{P}}
\def\Q{\cal{Q}}
\def\NN{\cal{N}}
\def\vco{\vartheta}
\def\tPhi{\tilde{\Phi}}

\newcommand{\m}[1]{
	\begin{bmatrix}
		#1 
	\end{bmatrix}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% {Author}{Email}{Date}
\footer{Dr. Phi Ha}{haphi@hus.edu.vn}{\today}
% {Paper Title}
\header{Example 2: triggering}

\begin{document}

% \lipsum

\begin{remark}
We notice that the presented theory above could not be trivially extended for high-index descriptor systems. To illustrate difficulties that could be arisen due to the high-index, we consider a system in Hessenberg form
%
\begin{equation}\label{eq6}
\begin{split}
\dot{x}_1(t) &= A_1 x_1 + A_2 x_2 + B_1 u, \\
0 &= A_3 x_1 + B_2 u, 
\end{split}
\end{equation}
%
where $A_3 A_2$ is nonsingular. This assumption implies that the DAE \eqref{eq6} has index two. Applying triggered feedback law $u(t) = u(t_k) = K x(t_k)$ for all $t \in [t_k,t_{k+1})$, we express the evolution of the closed-loop system on this interval by
the resulting system
%
\begin{equation}\label{eq7}
\begin{split}
\dot{x}_1(t) &= (A_1 + B_1 K_1) x_1 + (A_2 + B_1 K_2) x_2 + B_1 K_1 e_1(t)+ B_1 K_2 e_2(t), \\
0 &= (A_3 + B_2 K_1) x_1 + B_2 K_2 x_2 +  B_2  K_1 e_1(t)+  B_2  K_2 e_2(t). 
\end{split}
\end{equation}
%
We want to find a matrix K, and a event-triggered condition which generate triggering times $\{t_k\}_{k\in \N}$ such that system \eqref{eq7} 
is positive and stable. Furthermore, from the computational viewpoint, we also want to achieve a closed loop system of index 1.
Due to Lemma 2.6, we know that system \eqref{eq7} is positive if and only if $B_2 K_2$ is Hurwitz and $BK = \m{B_1 K_1 &  B_1 K_2 \\ B_2  K_1 & B_2  K_2} \succeq 0$. Furthermore, \eqref{eq7} is of index 1 if and only if $B_2 K_2$ is nonsingular. These conditions will strictly restrict the domain of applicable systems. 
Otherwise, one need to study positivity of index 2 system. This, however, is an open problem and will be discussed in upcoming research.
\end{remark}


\end{document}
