
\bibitem{b1} P. N. Boi,
{\it On the $\psi$-dichotomy for homogeneous
linear differential equations}, EJDE, Vol. 2006(2006), No. {\bf 40}, pp. 1--12..

\bibitem{b2} P. N. Boi,
{\it Existence of $\psi$-bounded solutions for nonhomogeneous linear
differential equations}, EJDE, Vol. 2007(2007), No. {\bf 52}, pp. 1--10.

\bibitem{c1} Constantin. A,
{\it Asymptotic properties of solution of differential equation},
Analele Universit$\tilde{a}$tii din Timisoara, Seria Stiinte
Matamatice, Vol. XXX, fasc. 2-3,1992, 183-225.

\bibitem{d1} Daletskii J. L., Krein M. G,
{\it Stability of solutions of differential equations in Banach spaces},
American Mathematical Society Providence, Rhode Island 1974.

\bibitem{d2} Dimandescu. A,
{\it Existence of $\psi$-bounded solutions for a system of differential
equations}, EJDE, Vol. 2004(2004), No.{\bf 63}, 1-6.

\bibitem{d3} Dimandescu. A,
{\it On the $\psi$-stability of a nonlinear volterra integro-differential
system}, Electron. J. Diff. Eqns., Vol. 2005(2005), No. {\bf 56}, 1-14.

\bibitem{d4} Dimandescu. A,
{\it Note on the $\psi$-boundedness of the solutions of a system
of differential equations}. Acta Math. Univ. Comenianea.
vol. LXXIII, {\bf 2}(2004), 223-233.

\bibitem{ms1} J. L. Massera and J. J. Schaffer;
\emph{Linear differential equations and functional analysis},
Ann. Math. 67 (1958), 517-573.

\bibitem{ms2} Massera J.J, Sch\" affer J.J, { ''Linear Differential Equations and
Function Spaces''}. Academic Press, New York 1966.
{J.  Math. Anal. Appl.} {\bf 261} (2001), 28-44.

\bibitem{AulMin}
B. Aulbach, N.V. Minh, { Nonlinear semigroups and the existence and 
	stability of semilinear nonautonomous evolution equations}, {\it 
	Abstract
	Appl. Anal.} {\bf 1} (1996), 351-380.
%%%%%%%
\bibitem{bajo} P. Bates, C. Jones, {\it Invariant manifolds for semilinear partial differential equations}, Dyn. Rep. {\bf 2} (1989) 1-38.
\bibitem{Ca} A.P. Calderon, {\it Spaces between $L^1$ and  $L^\infty$ and the theorem
	of Marcinkiewicz}, Studia Math. {\bf 26} (1996), 273-299.
\bibitem{chi} C.Chincone, "Ordinary differential equation", Springer-Verlag (1999)
\bibitem{DalKre} Ju. L. Daleckii, M. G. Krein, {  ''Stability of Solutions of Differential
	Equations in Banach Spaces"}. Transl. Amer. Math. Soc.  Provindence RI, {1974.}
\bibitem{Nag} 
K.J. Engel, R. Nagel, "One-parameter Semigroups for Linear Evolution Equations", 
Graduate Text Math. {\bf 194}, Springer-Verlag, Berlin-Heidelberg, 2000. 
\bibitem{hal} J. Hale, L.T. Magalh\~aes, W.M. Oliva, ``Dynamics in Infinite Dimensions", Appl. Math. Sci. {\bf
	47}, Springer-Verlag 2002.
\bibitem{Hen} D. Henry: {\it "Geometric Theory of Semilinear Parabolic 
	Equations",} Lecture Notes in Mathematics, No.~840, Springer, 
Berlin-Heidelberg-New York 1981.
\bibitem{HPM} N. Hirsch, C. Pugh, M. Shub, "Invariant Manifolds", Lect. Notes in Math., vol 183, Springer, New York, 1977.
\bibitem{Hu3} Nguyen Thieu Huy, {\it Exponential dichotomy of evolution
	equations and admissibility of function spaces on a half-line}, { J. Funct. Anal.} {\bf 235} (2006), 330-354.
%%%%%%%%%%%%%%%
\bibitem{Hu4} Nguyen Thieu Huy, {\it Stable manifold for evolution
	equations and admissibility of function spaces on a half-line}, { J. Diff. Equa.}, preprint.  
%%%%%%%%%%%%%%%%%%
\bibitem{LiTi} J. Lindenstrauss, L. Tzafriri, {''Classical Banach Spaces II, Function
	Spaces"}, Springer-Verlag, Berlin, 1979.
\bibitem{Ma} Martin, {" Nonlinear Operators and Differential Equations in Banach Spaces",}  Wiley Interscience, New York, 1976.
\bibitem{MaSc} Massera J.J, Sch\" affer J.J, { ''Linear Differential Equations and
	Function Spaces''}. Academic Press, New York 1966.
{J.  Math. Anal. Appl.} {\bf 261} (2001), 28-44. 
\bibitem{MRS} N.V. Minh,  F. R\"abiger,  R. Schnaubelt, {\it 
	Exponential stability,
	exponential expansiveness and exponential dichotomy of evolution equations on the
	half line}, { Integr. Eq. and Oper. Theory,} {\bf 32}(1998), 332-353.
\bibitem{MiWu} N.V. Minh, J. Wu, {\it Invariant manifolds of partial functional differential equations}, J. Diff. Eq. {\bf 198} (2004) 381-421. 
\bibitem{NaN}R. Nagel, G. Nickel, {\it Well-posedness for non-autonomous abtract Cauchy problems}.
Prog. Nonl. Diff. Eq. Appl. {\bf 50} (2002), 279-293.
\bibitem{Nic} G. Nickel, {\it On Evolution Semigroups and Wellposedness of non-autonomous Cauchy Problems}.
{ PhD Thesis, T\" ubingen, 1996.}
\bibitem{Nit}Nitecki, An Introduction to The Orbit Structure of Diffeomorphisms, MIT Press, Cambridge, MA, 1971.
\bibitem{Paz} A. Pazy, { ''Semigroup of Linear Operators and Application to Partial
	Differential Equations"}. Springer-Verlag, Berlin, 1983.
\bibitem{Per} O. Perron, {\it Die Stabilit\"atsfrage bei Differentialgleichungen}. 
{ Math. Z.} {\bf 32} (1930), 703-728.
\bibitem{RaSc} F. R\"abiger and R. Schaubelt, {\it The spectral mapping theorem for evolution
	semigroups on spaces of vector-valued functions},
Semigroup Forum {\bf 48} (1996), 225-239.
\bibitem{Sch} R. Schnaubelt, {\it Exponential Bounds and Hyperbolicity of Evolution Families}.
{ PhD Thesis, T\" ubingen, 1996.}
\bibitem{Sch3} R. Schnaubelt, {\it Exponential dichotomy of non-autonomous evolution equations},
Habil-\break itationsschrift, T\"ubingen, 1999.
\bibitem{Sch1} R. Schnaubelt, {\it Asymptotically autonomous parabolic evolution equations}.
{ J. Evol. Equ.} {\bf 1} (2001), 19-37.
\bibitem{SY} G.R. Sell, Y. You: {\it  "Dynamics of Evolutionary Equations",} Appl. Math. Sci. {\bf 143}, Springer-Verlag 2002.
\bibitem{Tr} H. Tribel, ''Interpolation Theory, Function Spaces, Differential
Operators", North-Holland, Amsterdam, New York, Oxford, 1978.